---
title: "Capstone Report (Final Draft)"
author: "Kendall Beaver"
date: "`r Sys.Date()`"
output: pdf_document
---

# Outline

## Demographics

## Qualitative Questions Analysis

## Test Score Analysis

## GenAI Results

```{r load_data, tidy=TRUE, message=FALSE, warning=FALSE, results='hide', echo=FALSE}

library(tidyr)
library(gridExtra)
library(readxl)
library(dplyr)
library(corrplot)
library(writexl)
library(ggplot2)
```

```{r separate_categories, tidy=TRUE, message=FALSE, warning=FALSE, results='hide', echo=FALSE}

lying <- read_excel("data/lying_data.xlsx")

library(dplyr)
library(tidyr)
library(ggplot2)

# Step 1: Reshape, include GROUP, relabel columns
type_of_lie_long <- lying %>%
  select(GROUP, QQ3_TYPE_OF_LIE, QQ3_LIE_2_SUMMARY) %>%
  pivot_longer(cols = c(QQ3_TYPE_OF_LIE, QQ3_LIE_2_SUMMARY),
               names_to = "QuestionType",
               values_to = "Response") %>%
  drop_na() %>%
  mutate(QuestionType = recode(QuestionType,
                               QQ3_TYPE_OF_LIE = "Before Ad",
                               QQ3_LIE_2_SUMMARY = "After Ad"))

# Step 2: Count and calculate percentages for each GROUP
lie_counts <- type_of_lie_long %>%
  group_by(GROUP, QuestionType, Response) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(GROUP, QuestionType) %>%
  mutate(perc = n / sum(n) * 100)

# Step 3: Set factor levels for consistent x-axis order
lie_counts$QuestionType <- factor(lie_counts$QuestionType, levels = c("Before Ad", "After Ad"))

# Step 4: Create one plot per GROUP
plot_list <- lapply(unique(lie_counts$GROUP), function(g) {
  ggplot(filter(lie_counts, GROUP == g), aes(x = QuestionType, y = n, fill = Response)) +
    geom_bar(stat = "identity", position = "stack") +
    geom_text(aes(label = paste0(round(perc, 1), "%")),
              position = position_stack(vjust = 0.5),
              size = 3,
              color = "black") +
    labs(title = paste("Group:", g),
         x = "\nResponses",
         y = "Count") +
    theme_minimal() #+
    #theme(axis.text.x = element_text(angle = 15, hjust = 1))
})

# Step 5: Print each plot
plot_list[[1]]  # Control Group (Visual)
plot_list[[2]]  # Test Group (Visual)
plot_list[[3]]  # Control Group (Audio)
plot_list[[4]]  # Test Group (Audio)
```

While the Test Group (Audio) went from 7.1% to 14.3%, everything stayed exactly the same except for "Unsure."

The Control Group (Audio) seems to have had some effect on the getting respondants to put a different answer, "Keeping friend from danger and/or punishment" to "White Lie," dropping by 25% and increasing by 7.8%.

```{r itmist_box_2, tidy=TRUE, message=FALSE, warning=FALSE, results='hide', echo=FALSE, fig.align='center', results='asis'}

# Define custom labels for groups
group_titles <- c(
  "1" = "VISUAL AD", # Test Group (Visual)
  "2" = "VISUAL AD", # Control Group (Visual)
  "3" = "AUDIO AD", # Test Group (Audio)
  "4" = "AUDIO AD" # Control Group (Audio)
)

# Reshape the data to long format for easier faceting
long_data <- misinfo_filtered %>%
  # Convert both "ITMIST PRE SCORE" and "ITMIST POST SCORE" to numeric
  mutate(
    `ITMIST PRE SCORE` = as.numeric(`ITMIST PRE SCORE`),
    `ITMIST POST SCORE` = as.numeric(`ITMIST POST SCORE`)
  ) %>%
  select(GROUP, `ITMIST PRE SCORE`, `ITMIST POST SCORE`) %>%  # Updated column names here
  pivot_longer(cols = c(`ITMIST PRE SCORE`, `ITMIST POST SCORE`), 
               names_to = "Test_Time", 
               values_to = "Score") %>%
  mutate(Test_Time = factor(Test_Time, levels = c("ITMIST PRE SCORE", "ITMIST POST SCORE")))  # Updated levels

# Create the plot for Groups 2 and 4 (Control Group)
plot2 <- ggplot(long_data %>% filter(GROUP %in% c(2, 4)), aes(x = Test_Time, y = Score, fill = Test_Time)) +
  geom_boxplot(outlier.colour = "red", outlier.shape = 16, outlier.size = 2) +
  facet_wrap(~ GROUP, labeller = as_labeller(group_titles)) +  # Only for Groups 2 and 4
  labs(
    title = "ITMIST Scores Before & After Ad - Control Group\n",  # Updated title for ITMIST
    x = "\nITMIST Test Scores",  # Updated axis label for ITMIST
    y = "Score\n"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    legend.position = "none"
  )

# Use grid.arrange to display the plot
grid.arrange(plot2)  # Display the plot for Control Groups (2 & 4)
```

# Analysis of QQ3:

This didn't effect anybody across all of the categories.

```{r table_of_previous, tidy=TRUE, message=FALSE, warning=FALSE, results='hide', echo=FALSE, fig.align='center', results='asis'}

library(knitr)

library(tidyr)

lie_counts_wide <- lie_counts %>%
  select(GROUP, QuestionType, Response, n) %>%
  pivot_wider(names_from = Response, values_from = n, values_fill = 0)

# Then use gt or kable
lie_counts_wide %>%
  gt()

```
